Assessing Fire Response Efficiency and the Crucial Role of Protection Systems in Reducing Damage

### 2024-09-23 paper/paper.qmd
fix grammar error

# Introduction {#sec-intro}
The urban fire hazard is one of the most pressing issues in this context, especially in Canada where cities are dealing with such issues like climate, facilities or population density.As of July 1 2023, the population in urban area in Canada reached 33,812,133 [@statsCanada]. 
Not only do fires in highly populated regions result in heavy losses in terms of property, but also, in the contest of people and the environment, the consequences are enormous. Also, urban fires are resources-dependent and require attention from city services and emergency services, thus indicating the need for prevention, action and planning based on risk assessment. With such issues in mind, the knowledge of urban fire hazards in Canadian cities is needed for creating policies that address public safety and increase urban resilience.

>>>>

# Introduction {#sec-intro}
The urban fire hazard is one of the most pressing issues in this context, especially in Canada where cities are dealing with such issues like climate, facilities or population density. As of July 1 2023, the population in urban area in Canada reached 33,812,133 [@statsCanada]. 
Not only do fires in highly populated regions result in heavy losses in terms of property, but also, in the contest of people and the environment, the consequences are enormous. Also, urban fires are resources-dependent and require attention from city services and emergency services, thus indicating the need for prevention, action and planning based on risk assessment. With such issues in mind, the knowledge of urban fire hazards in Canadian cities is needed for creating policies that address public safety and increase urban resilience.
